### 2023-09-02 sections/2-methods.tex
removed quicksort partition

To find this element, 
we use a process similar to the Partition algorithm used in Quicksort~\cite{10.1093/comjnl/5.1.10}, adjusted to account for the varying cardinalities of elements in $Q$. 
Our modified version of this algorithm (see Algorithm 4) finds the smallest index $i$ such 
that all elements in $Q$ with $\delta_{max}$ closer to or equal to $Q[i]$'s $\delta_{max}$ collectively have cardinality greater
than or equal to $k$. We consider $Q[i]$ to be our $q_{\tau}$, and our threshold 
$\tau$ to be $Q[i]$'s $\delta_{max}$.

@@

\begin{algorithm} % enter the algorithm environment
    \caption{QuicksortPartition(\emph{Q, k, l, r})} % give the algorithm a caption
    \label{alg:quicksort-partition} % and a label for \ref{} commands later in the document
    \begin{algorithmic}[5] % enter the algorithmic environment
        \IF{$l \geq r$}
            \STATE Return $min(l, r)$
        \ELSE 
            \STATE $pivot = l + (r - l) / 2$
            \STATE $Q.swap(pivot, r)$
            \STATE $a \Leftarrow l$
            \STATE $b \Leftarrow l$
            \WHILE {$b < r$}
                \IF {$Q[b].\delta_{max} < Q[r].\delta_{max}$}
                    \STATE $Q.swap(a, b)$
                    \STATE $a \Leftarrow a + 1$
                \ENDIF
                \STATE $b \Leftarrow b + 1$
            \ENDWHILE
            \STATE $Q.swap(a, r)$
            \STATE $p \Leftarrow r$
            \STATE $g \Leftarrow \sum_{i=0}^{p} |Q[i]|$
            \IF {$g = k$}
                \STATE Return $p$
            \ELSIF {$g < k$}
                \STATE $QuicksortPartition(Q, k, p + 1, r)$
            \ELSE 
                \IF {$p > 0 \land g > k + |Q[p - 1]|$}
                    \STATE $QuicksortPartition(Q, k, l, p - 1)$
                \ELSIF {$p > 0 \land g = k + |Q[p - 1]|$}
                    \STATE Return $p - 1$
                \ELSE
                    \STATE Return $p$
                \ENDIF
            \ENDIF
        \ENDIF
    \end{algorithmic}
    \end{algorithm}

@@

\subsubsection{Complexity of Sieve, Sieve with Separate Centers, and Greedy Sieve}
\label{paragraph:methods:sieve-complexity}

>>>>

To find this element, 
we use a process similar to the Partition algorithm used in Quicksort~\cite{10.1093/comjnl/5.1.10}, adjusted to account for the varying cardinalities of elements in $Q$. 
Our modified version of this algorithm finds the smallest index $i$ such 
that all elements in $Q$ with $\delta_{max}$ closer to or equal to $Q[i]$'s $\delta_{max}$ collectively have cardinality greater
than or equal to $k$. We consider $Q[i]$ to be our $q_{\tau}$, and our threshold 
$\tau$ to be $Q[i]$'s $\delta_{max}$.

@@

@@

\subsubsection{Complexity of Sieve Algorithms}
\label{paragraph:methods:sieve-complexity}
